### 2020-11-21 pldi21/case-studies.tex
fix sec 4 at page 10

\subsubsection{Closure Collection} The subtlety is that 
evaluation in Hazel is defined for closed expressions as usual,
but parameters and splices can be open, i.e. refer to surrounding variables. 
To provide a environment that binds these variables, 
Hazel performs \textbf{closure collection} in two phases.

>>>>

\subsubsection{Closure Collection}\label{sec:closure-collection-example} The subtlety is that 
evaluation in Hazel is defined for closed expressions as usual,
but parameters and splices can be open, i.e. refer to surrounding variables. 
To provide a environment that binds these variables, 
Hazel performs \textbf{closure collection} in two phases.
